Models

### 2023-10-03 analysis/models.qmd
finally ran the model

library(tidyverse)
library(ordinal)
library(marginaleffects)
library(modelsummary)
library(brms)
library(tidybayes)
library(broom.mixed)
library(ggplot2)
library(ggdist)
library(broom)
library(here)

@@

@@

mrs_90_ich_lat <- clm(
  mrs_90 ~ ich_laterality,
  data = data,
  link = "logit"
)

neurosurg_ich_lat <- clm(
  neurosurgery_evac ~ ich_laterality,
  data = data,
  link = "logit"
)

mrs_90_ich_lat_neurosurg <- clm(
  mrs_90 ~ ich_laterality + neurosurgery_evac,
  data = data,
  link = "logit"
)

summary(mrs_90_ich_lat)
summary(neurosurg_ich_lat)
summary(mrs_90_ich_lat_neurosurg)

@@

```{r bayesian ordinal}

fit1 <- brm(
  data = data,
  family = cumulative(probit),
  mrs_90 ~ 1,
)

fit2 <- brm(
  data = data,
  family = cumulative(logit),
  mrs_90 ~ 1,
)

fit3 <- brm(
  data = data,
  family = cumulative(logit),
  mrs_90 ~ ich_laterality,
)

print(fit1)
print(fit2)
print(fit3)

pred <- predictions(fit3)

>>>>

library(tidyverse)
library(ordinal)
library(marginaleffects)
library(modelsummary)
library(brms)
library(cmdstanr)
library(tidybayes)
library(broom.mixed)
library(ggplot2)
library(ggdist)
library(broom)
library(gt)
library(here)

options(mc.cores = parallel::detectCores())

@@

data$ich_location <- fct_drop(data$ich_location)
table(data$ich_location)

@@

fit_freq <- clm(
  mrs_90 ~ ich_laterality + age + ich_location + ich_volume_baseline + gcs_baseline + neurosurgery_evac,
  data = data,
  link = "logit"
)

summary(fit_freq)

predictions(fit_freq, by = "ich_laterality", type = "cum.prob") |>
  gt()

predictions(fit_freq, by = c("ich_location", "ich_laterality"), type = "cum.prob") |>
  gt()

plot_predictions(fit_freq, condition = c("ich_location", "ich_laterality"), type = "cum.prob")

tidy(fit_freq)

@@

```{r bayesian ordinal, warning=FALSE, message=FALSE}

fit_brms <- brm(
  mrs_90 ~ ich_laterality + age + ich_location + ich_volume_baseline + gcs_baseline + neurosurgery_evac,
  data = data,
  family = cumulative(logit),
  prior = set_prior("normal(0,5)"),
  chains = 2,
  cores = 6,
  backend = "cmdstanr"
)

print(fit_brms)

tidy(fit_brms) |>
  select(c(estimate, conf.low, conf.high))

predictions(fit_brms, by = c("ich_location", "ich_laterality"), type = "response") |>
  gt()

plot_predictions(fit_brms, condition = c("ich_location", "ich_laterality"), type = "response")

plot_predictions(fit_brms, condition = c("ich_location", "ich_laterality"), type = "prediction")
